---
title: "LinReg"
author: "Hussnain Ali"
#output: rmarkdown::html_vignette
output: rmarkdown::html_document

vignette: >
  %\VignetteIndexEntry{LinReg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r echo=TRUE }
library(LabAssignment4)
```

Here we Load data Set and create an object of the class of this package and then we call the print method of that class with that object

```{r echo=TRUE}
data(iris)
tempObj <- linreg$new(Petal.Length~Species, data = iris)
tempObj$print()
```

This class has plot() method that return the Plots.

```{r echo=TRUE}
tempObj$plot()
```

This class has resid() method that return the vector of residuals eˆ.

```{r echo=TRUE}
tempObj$resid()
```

This class has pred() method return the predicted values yˆ.

```{r echo=TRUE}
tempObj$pred()
```

This class has coef() method return the coefficients as a named vector.

```{r echo=TRUE}
tempObj$coef()
```

This class has summary() method return a similar printout as printed for lm objects, but you only need to present the coefficients with their standard error, t-value and p-value as well as the estimate of σˆ and the degrees of freedom in the model.

```{r echo=TRUE}
tempObj$summary()
```
